Stimuli List Generation

### 2023-03-06 Stimuli List and Data Source/Stimuli List Generation.Rmd
Updated stimuli list code to use for loops

#Loading needed packages

@@

Phrase_List_1 <- rio::import("Phrase List 1.xlsx")
Phrase_List_2 <-rio::import("Phrase List 2.xlsx")

# randomize order of list 1

set.seed(1000)
Phrase_List_1_random <- Phrase_List_1[sample(1:nrow(Phrase_List_1)), ]

# Randomize order of list 2

set.seed(7036)
Phrase_List_2_random <- Phrase_List_2[sample(1:nrow(Phrase_List_2)), ]

# create data frame for 5 practice trials

@@

# Adding 5 practice trials to the beginning of new list one

List_1_New <- dplyr::full_join(Practice_trials, Phrase_List_1_random) %>%
  dplyr::relocate(., targetPhrase, .after = speaker) %>%
  dplyr::relocate(., code, .before = speaker) %>%
  #creating new trial number, block number, and counter balance variables
  dplyr::mutate(., trial = row_number(),
                counterBalance = 1,
                block = ifelse(speaker == "Practice", 1, ceiling((row_number() - 5)/ 10) + 1),
                practiceTrial = ifelse(speaker == "Practice", "Practice", "Experimental")) %>%
  #moving new variables in the data frame
  dplyr::relocate(trial, .before = code) %>%
  dplyr::relocate(block, .before = counterBalance) %>%
  dplyr::relocate(practiceTrial, .after = targetPhrase)

# Adding 5 practice trials to beginning of new list 2

List_2_New <- dplyr::full_join(Practice_trials, Phrase_List_2_random) %>%
  dplyr::relocate(., targetPhrase, .after = speaker) %>%
  dplyr::relocate(., code, .before = speaker) %>%
  #creating new trial, block number, and counter balance variables
  dplyr::mutate(., trial = row_number(),
                counterBalance = 2,
                block = ifelse(speaker == "Practice", 1, ceiling((row_number() - 5) /10) + 1),
                practiceTrial = ifelse(speaker == "Practice", "Practice", "Experimental")) %>%
  # relocating new variables in data frame
  dplyr::relocate(trial, .before = code) %>%
  dplyr::relocate(block, .before = counterBalance) %>%
  dplyr::relocate(practiceTrial, .after = targetPhrase)

#exporting the separate phrase lists in excel (used to eventually create RA stimuli lists in word)

rio::export(List_1_New, "Phrase List 1 New.xlsx")
rio::export(List_2_New, "Phrase List 2 New.xlsx")

## removing objects that are no longer needed from environment

rm(Phrase_List_1_random, Phrase_List_2_random, Phrase_List_1, Phrase_List_2, Practice_trials)

@@

## Creating the DataSource file

@@

DataSource <- dplyr::full_join(List_1_New, List_2_New)

@@

rm(List_1_New, List_2_New)

>>>>

@@

#Creating Practice Trials dataframe

@@

# Setting up a loop for randomizing stimuli lists

file_names <- c("Phrase List 1.xlsx", "Phrase List 2.xlsx")
seed = c(1000, 7036)

for (i in seq_along(file_names))  {

  data <- rio::import(file_names[i])
  set.seed(seed[i])
  #Randomize the data
  data_random <- data[sample(1:nrow(data)), ]

  #Merging the practice trials df with the randomized list df
  data_random <- dplyr::full_join(Practice_trials, data_random) %>%
    dplyr::relocate(., targetPhrase, .after = speaker) %>%
    dplyr::relocate(., code, .before = speaker) %>%
    #creating new trial number, block number, and counter balance variables
    dplyr::mutate(., trial = row_number(), 
                  counterBalance = i, 
                  block = ifelse(speaker == "Practice", 1, ceiling((row_number() - 5)/ 10) + 1), 
                  practiceTrial = ifelse(speaker == "Practice", "Practice", "Experimental")) %>%
    #moving new variables in the data frame
    dplyr::relocate(trial, .before = code) %>%
    dplyr::relocate(block, .before = counterBalance) %>%
    dplyr::relocate(practiceTrial, .after = targetPhrase)

  # Renaming the new dfs
  data_name <- paste("newList", i, sep = "")
  assign(data_name, data_random)

  # Exporting dfs (to create stimuli lists in word)
  rio::export(data_random, paste("New_Phrase_List", i, ".csv"))
}

# Removing unneeded items from environment

rm(data, data_random, Practice_trials, data_name, file_names, i, seed)

@@

# Creating the DataSource file

@@

DataSource <- dplyr::full_join(newList1, newList2)

@@

rm(newList1, newList2)
